---
title: "A lot of analysis"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(magrittr)
```

## Read in the data

Due to the inconsistent column naming covention, we manually convert the cx column to cX in an effort to reduce obfuscation.

```{r read data}
# Read in the data
data <- read.csv('Greatest_Aussie_Groceries_sales_data.csv', header=TRUE, sep=",")
# Change column name of cx to match style of capital X and Y
colnames(data)[colnames(data)=="cx"] <- "cX"
```

### Reformatting Data
```{r}
# Organic X
dataR <- data %>% filter(class=="organic") %>% select(STORE, WEEK, Hval_150, pX, cX, oz_X, deal_X, feat_X)
dataR$brand <- "X"
dataR$class <- "organic"
colnames(dataR) <- c("STORE", "WEEK", "Hval", "p", "c", "oz", "deal", "feat", "brand", "class")
data.ref <- dataR
# Organic Y
dataR <- data %>% filter(class=="organic") %>% select(STORE, WEEK, Hval_150, pY, cY, oz_Y, deal_Y, feat_Y)
dataR$brand <- "Y"
dataR$class <- "organic"
colnames(dataR) <- c("STORE", "WEEK", "Hval", "p", "c", "oz", "deal", "feat", "brand", "class")
data.ref <- rbind(data.ref, dataR)
# NonOrganic X
dataR <- data %>% filter(class=="nonorganic") %>% select(STORE, WEEK, Hval_150, pX, cX, oz_X, deal_X, feat_X)
dataR$brand <- "X"
dataR$class <- "nonorganic"
colnames(dataR) <- c("STORE", "WEEK", "Hval", "p", "c", "oz", "deal", "feat", "brand", "class")
data.ref <- rbind(data.ref, dataR)
# NonOrganic Y
dataR <- data %>% filter(class=="nonorganic") %>% select(STORE, WEEK, Hval_150, pY, cY, oz_Y, deal_Y, feat_Y)
dataR$brand <- "Y"
dataR$class <- "nonorganic"
colnames(dataR) <- c("STORE", "WEEK", "Hval", "p", "c", "oz", "deal", "feat", "brand", "class")
data.ref <- rbind(data.ref, dataR)
```

## Mutate Data

We mutate the data to include columns for deal_feat (an indictator for both deal and features), revenue, and profit.

```{r mutate new columns}
# Append a deal_feat column for X and Y
data <- mutate(data, deal_feat_Y = deal_Y*10 + feat_Y, deal_feat_X = deal_X*10 + feat_X)
# Append a revenue column for X and Y 
data <- mutate(data, rev_X = oz_X * pX, rev_Y = oz_Y * pY)
# Append a profit column for X and Y 
data <- mutate(data, profit_X = rev_X - cX * pX, profit_Y = rev_Y - cY * pY)
```

## Summary Plots

Lets start by just plotting the profit over the 52 weeks for each store. 

```{r plot, warning=FALSE}
plotStore <- function(store_ID) {
# The palette with black:
cbbPalette <- c("red4", "orange1", "blue4", "skyblue1", "green4", "chartreuse1", "darkorchid4", "mediumorchid1")
# Pull data into temp results dataframe
results <- data.frame(WEEK=c(1:52))
results[,c("profit_X_org","profit_Y_org")] <- data %>% filter(.,STORE==store_ID, class=="organic") %>% select(.,profit_X, profit_Y)
results[,c("profit_X_non","profit_Y_non")] <- data %>% filter(.,STORE==store_ID, class=="nonorganic") %>% select(.,profit_X, profit_Y)
results[,c("profit_X_org_col","profit_Y_org_col")] <- data %>% filter(.,STORE==store_ID, class=="organic") %>% select(.,deal_X, deal_Y)
results[,c("profit_X_non_col","profit_Y_non_col")] <- data %>% filter(.,STORE==store_ID, class=="nonorganic") %>% select(.,deal_X, deal_Y)
# Assign legend name to categorical data
results$profit_X_org_col[results$profit_X_org_col == 0] <- "X organic w/o deal"
results$profit_X_org_col[results$profit_X_org_col == 1] <- "X organic w/ deal"
results$profit_Y_org_col[results$profit_Y_org_col == 0] <- "Y organic w/o deal"
results$profit_Y_org_col[results$profit_Y_org_col == 1] <- "Y organic w deal"
results$profit_X_non_col[results$profit_X_non_col == 0] <- "X nonorganic w/o deal"
results$profit_X_non_col[results$profit_X_non_col == 1] <- "X nonorganic w deal"
results$profit_Y_non_col[results$profit_Y_non_col == 0] <- "Y nonorganic w/o deal"
results$profit_Y_non_col[results$profit_Y_non_col == 1] <- "Y nonorganic w deal"
# Plot results
ggplot(results, aes(x=WEEK)) + 
  geom_point(aes(y=profit_X_org, colour=profit_X_org_col)) +
  geom_point(aes(y=profit_Y_org, colour=profit_Y_org_col)) + 
  geom_point(aes(y=profit_X_non, colour=profit_X_non_col)) +
  geom_point(aes(y=profit_Y_non, colour=profit_Y_non_col)) + 
  scale_colour_manual(values=cbbPalette) +
  labs(x = "Week", y = "Profit", title = paste("Profit for Store",store_ID)) 
}

# Plot the data
plotStore(1)
plotStore(2)
plotStore(3)
plotStore(4)
plotStore(5)
plotStore(6)
plotStore(7)

## General Scatter Plot
cbbPalette <- c("red4", "orange1", "blue4", "skyblue1", "green4", "chartreuse1", "darkorchid4", "mediumorchid1")
generalScatterResults <- data.ref %>% select(WEEK, p, c, oz, deal, class, brand)
generalScatterResults$deal[generalScatterResults$deal == 1] = "w deal"
generalScatterResults$deal[generalScatterResults$deal == 0] = "w/o deal"
generalScatterResults <- generalScatterResults %>% mutate(profit=oz*(p-c))
generalScatterResults <- generalScatterResults %>% mutate(type=paste(brand,class,deal,sep=" "))
ggplot(generalScatterResults, aes(x=WEEK)) + 
  geom_point(aes(y=profit, colour=type)) +
  scale_colour_manual(values=cbbPalette) +
  labs(x = "Week", y = "Profit", title = "Profit for products across all stores") 
```

# Box plots of profit for the different products
This is just a simple box plot analysis
```{r}
# Function to retreve data from dataframe and composite into factor
retrieveData <- function(data, deal, CLASS, xy) {
  names <- c("STORE", "PROFIT")
  if (xy == "x")
    temp <- data %>% filter(deal_X==deal, class==CLASS) %>% select(STORE, profit_X)
   else
    temp <- data %>% filter(deal_Y==deal, class==CLASS) %>% select(STORE, profit_Y)
  colnames(temp) <- names
  name <- if (xy == "x") "X" else "Y"
  name <- if (CLASS == "organic") paste(name,"O",sep="") else paste(name,"I",sep="") 
  name <- if (deal == 1) paste(name,"deal",sep="_") else paste(name,"no_deal",sep="_") 
  return(data.frame(type=rep(name,nrow(temp)),temp))
}

boxplot_data <- retrieveData(data, deal=0, CLASS="organic", xy="x")
boxplot_data <- rbind(boxplot_data,retrieveData(data, deal=0, CLASS="nonorganic", xy="x"))
boxplot_data <- rbind(boxplot_data,retrieveData(data, deal=0, CLASS="organic", xy="y"))
boxplot_data <- rbind(boxplot_data,retrieveData(data, deal=0, CLASS="nonorganic", xy="y"))
boxplot_data <- rbind(boxplot_data,retrieveData(data, deal=1, CLASS="organic", xy="x"))
boxplot_data <- rbind(boxplot_data,retrieveData(data, deal=1, CLASS="nonorganic", xy="x"))
boxplot_data <- rbind(boxplot_data,retrieveData(data, deal=1, CLASS="organic", xy="y"))
boxplot_data <- rbind(boxplot_data,retrieveData(data, deal=1, CLASS="nonorganic", xy="y"))

ggplot(boxplot_data, aes(x=type, y=PROFIT)) + geom_boxplot() + labs(title="Boxplots of profit for different products", x="Product", y = "Profit")
```

Given the massive spread between no deal and deal data, let's take a log10() scale transform of the y-axis

```{r, results='asis'}
boxplot_data <- mutate(boxplot_data, log10PROFIT=log10(PROFIT))
ggplot(boxplot_data, aes(x=type, y=log10PROFIT)) + geom_boxplot() + labs(title="Boxplots of log10(profit) for different products", x="Product", y = "log10(Profit)")
```

It is clear from these boxplots that the median values for X and Y products are approximately equal. The spread of profit for Y is much larger than X. Profit increases dramatically when a deal is going on.

Just as an additional spam of figures, lets look at the box plots for each product seperated by store (again with a log10 scaling)

```{r}
boxplot_data %>% filter(type=="XO_no_deal") %>% ggplot(., aes(x=STORE, y=PROFIT)) + geom_boxplot(aes(group = cut_width(STORE, 1))) + labs(title=paste("Profit of", "XO_no_deal" ,"for different stores"), x="Store", y = "Profit")
boxplot_data %>% filter(type=="XI_no_deal") %>% ggplot(., aes(x=STORE, y=PROFIT)) + geom_boxplot(aes(group = cut_width(STORE, 1))) + labs(title=paste("Profit of", "XI_no_deal" ,"for different stores"), x="Store", y = "Profit")
boxplot_data %>% filter(type=="YO_no_deal") %>% ggplot(., aes(x=STORE, y=PROFIT)) + geom_boxplot(aes(group = cut_width(STORE, 1))) + labs(title=paste("Profit of", "YO_no_deal" ,"for different stores"), x="Store", y = "Profit")
boxplot_data %>% filter(type=="YI_no_deal") %>% ggplot(., aes(x=STORE, y=PROFIT)) + geom_boxplot(aes(group = cut_width(STORE, 1))) + labs(title=paste("Profit of", "YI_no_deal" ,"for different stores"), x="Store", y = "Profit")
boxplot_data %>% filter(type=="XO_deal") %>% ggplot(., aes(x=STORE, y=PROFIT)) + geom_boxplot(aes(group = cut_width(STORE, 1))) + labs(title=paste("Profit of", "XO_deal" ,"for different stores"), x="Store", y = "Profit")
boxplot_data %>% filter(type=="XI_deal") %>% ggplot(., aes(x=STORE, y=PROFIT)) + geom_boxplot(aes(group = cut_width(STORE, 1))) + labs(title=paste("Profit of", "XI_deal" ,"for different stores"), x="Store", y = "Profit")
boxplot_data %>% filter(type=="YO_deal") %>% ggplot(., aes(x=STORE, y=PROFIT)) + geom_boxplot(aes(group = cut_width(STORE, 1))) + labs(title=paste("Profit of", "YO_deal" ,"for different stores"), x="Store", y = "Profit")
boxplot_data %>% filter(type=="YI_deal") %>% ggplot(., aes(x=STORE, y=PROFIT)) + geom_boxplot(aes(group = cut_width(STORE, 1))) + labs(title=paste("Profit of", "YI_deal" ,"for different stores"), x="Store", y = "Profit")
```


## Regression
```{r}
# Function that pulls out the data
retrieveDataLM <- function(data, CLASS, xy) {
  names <- c("STORE", "oz", "p", "deal")
  if (xy == "x")
    temp <- data %>% filter(.,class==CLASS) %>% select(.,STORE, oz_X, pX, deal_X)
  else
    temp <- data %>% filter(class==CLASS) %>% select(STORE, oz_Y, pY, deal_Y)
  colnames(temp) <- names
  name <- if (xy == "x") "X" else "Y"
  name <- if (CLASS == "organic") paste(name,"O",sep="") else paste(name,"I",sep="") 
  return(data.frame(type=rep(name,nrow(temp)),temp))
}

# Function that plots the loglog and actual curves
filteredLM <- function(data, TYPE, log=FALSE, include_Deal=FALSE) {
  response <- data %>% filter(type==TYPE) %>% select(oz) %>% {if (log) log(.) else (.)} %>% as.matrix()
  elasticity <- data %>% filter(type==TYPE) %>% select(p) %>% {if (log) log(.) else (.)} %>% as.matrix()
  deal <- data %>% filter(type==TYPE) %>% select(deal) %>% {if (include_Deal) (.) else (.)*0} %>% as.matrix()
  return(lm(response~elasticity+deal))
}

# Function to plot Prediction with actual data
plotStatsLogLog <- function(lm, type="loglog", title="") {
  results <- data.frame(p=lm$model$elasticity, oz=lm$model$response, resid=resid(lm))
  results <- mutate(results, loglogSol=lm$coefficients[1] + lm$coefficients[2]*p + if (is.na(lm$coefficients[3])) 0 else lm$coefficients[3]*lm$model$deal)
  results$sol <- exp(results$loglogSol)
  if (type == "loglog")
    ggplot(results) + geom_point(aes(x=p, y=oz)) + geom_line(aes(x=p, y=loglogSol)) + labs(x="log(price)", y="log(oz)", title=title) + coord_flip()
  else
    ggplot(results) + geom_point(aes(x=exp(p), y=exp(oz))) + geom_line(aes(x=exp(p), y=sol))  + labs(x="price", y="oz", title=title) + coord_flip()
}

# Function that generates the inear model
lm_data <- retrieveDataLM(data, CLASS="organic", xy="x")
lm_data <- rbind(lm_data,retrieveDataLM(data, CLASS="nonorganic", xy="x"))
lm_data <- rbind(lm_data,retrieveDataLM(data, CLASS="organic", xy="y"))
lm_data <- rbind(lm_data,retrieveDataLM(data, CLASS="nonorganic", xy="y"))
```

### Log Regression for Organic X without deal dummy variable
Linear regression for $\log(oz_{x-org}) = \log(k) + r \log(p_{x-org})$
```{r}
# Linear Model Summary for Organic X product without including the deal dummy variable
XO_lm_without_deal <- filteredLM(lm_data, TYPE="XO", log=TRUE, include_Deal=FALSE)
summary(XO_lm_without_deal)
plotStatsLogLog(XO_lm_without_deal, "loglog", "loglog PED for Organic X without deal")
plotStatsLogLog(XO_lm_without_deal, "normal", "PED for Organic X without deal")
```

### Log Regression for Organic X with deal dummy variable
Linear regression for $\log(oz_{x-org}) = \log(k) + r \log(p_{x-org}) + deal_{x-org}$
```{r}
# Linear Model Summary for Organic X product including deal dummy variable
XO_lm_with_deal <- filteredLM(lm_data, TYPE="XO", log=TRUE, include_Deal=TRUE)
summary(XO_lm_with_deal)
plotStatsLogLog(XO_lm_with_deal, "loglog", "loglog PED for Organic X with deal")
plotStatsLogLog(XO_lm_with_deal, "normal", "PED for Organic X with deal")
```

### Log Regression for Organic Y without deal dummy variable
Linear regression for $\log(oz_{y-org}) = \log(k) + r \log(p_{y-org})$
```{r}
# Linear Model Summary for Organic Y product without including the deal dummy variable
YO_lm_without_deal <- filteredLM(lm_data, TYPE="YO", log=TRUE, include_Deal=FALSE)
summary(YO_lm_without_deal)
plotStatsLogLog(YO_lm_without_deal, "loglog", "loglog PED for Organic Y without deal")
plotStatsLogLog(YO_lm_without_deal, "normal", "PED for Organic Y without deal")
```

### Log Regression for Organic Y with deal dummy variable
Linear regression for $\log(oz_{y-org}) = \log(k) + r \log(p_{y-org}) + deal_{y-org}$
```{r}
# Linear Model Summary for Organic Y product including deal dummy variable
YO_lm_with_deal <- filteredLM(lm_data, TYPE="YO", log=TRUE, include_Deal=TRUE)
summary(YO_lm_with_deal)
plotStatsLogLog(YO_lm_with_deal, "loglog", "loglog PED for Organic Y with deal")
plotStatsLogLog(YO_lm_with_deal, "normal", "PED for Organic Y with deal")
```

### Log Regression for Nonorganic X without deal dummy variable
Linear regression for $\log(oz_{x-nonorg}) = \log(k) + r \log(p_{x-nonorg})$
```{r}
# Linear Model Summary for Nonorganic X product without including the deal dummy variable
XI_lm_without_deal <- filteredLM(lm_data, TYPE="XI", log=TRUE, include_Deal=FALSE)
summary(XI_lm_without_deal)
plotStatsLogLog(XI_lm_without_deal, "loglog", "loglog PED for Nonorganic X without deal")
plotStatsLogLog(XI_lm_without_deal, "normal", "PED for Nonrganic X without deal")
```

### Log Regression for Nonorganic X with deal dummy variable
Linear regression for $\log(oz_{x-nonorg}) = \log(k) + r \log(p_{x-nonorg}) + deal_{x-nonorg}$
```{r}
# Linear Model Summary for Nonorganic X product including deal dummy variable
XI_lm_with_deal <- filteredLM(lm_data, TYPE="XI", log=TRUE, include_Deal=TRUE)
summary(XI_lm_with_deal)
plotStatsLogLog(XI_lm_with_deal, "loglog", "loglog PED for Nonorganic X with deal")
plotStatsLogLog(XI_lm_with_deal, "normal", "PED for Nonorganic X with deal")
```

### Log Regression for Nonorganic Y without deal dummy variable
Linear regression for $\log(oz_{y-nonorg}) = \log(k) + r \log(p_{y-nonorg})$
```{r}
# Linear Model Summary for Nonorganic Y product without including the deal dummy variable
YI_lm_without_deal <- filteredLM(lm_data, TYPE="YI", log=TRUE, include_Deal=FALSE)
summary(YI_lm_without_deal)
plotStatsLogLog(YI_lm_without_deal, "loglog", "loglog PED for Nonorganic Y without deal")
plotStatsLogLog(YI_lm_without_deal, "normal", "PED for Nonorganic Y without deal")
```

### Log Regression for Nonorganic Y with deal dummy variable
Linear regression for $\log(oz_{y-nonorg}) = \log(k) + r \log(p_{y-nonorg}) + deal_{y-nonorg}$
```{r}
# Linear Model Summary for Nonorganic Y product including deal dummy variable
YI_lm_with_deal <- filteredLM(lm_data, TYPE="YI", log=TRUE, include_Deal=TRUE)
summary(YI_lm_with_deal)
plotStatsLogLog(YI_lm_with_deal, "loglog", "loglog PED for Nonorganic Y with deal")
plotStatsLogLog(YI_lm_with_deal, "normal", "PED for Nonorganic Y with deal")
```

## Cross Elasticity of demand 
```{r}
# Function that pulls out the data
retrieveDataCPED <- function(data, Q_class, Q_brand) {
tempQ <- data %>% filter(., class==Q_class) %>% select(., STORE, matches(paste("oz",Q_brand,sep="_")))
colnames(tempQ) <- c("STORE", "oz")
tempP_Org <- data %>% filter(., class=="organic") %>% select(., pX, pY)
colnames(tempP_Org) <- c("p_X_org", "p_Y_org")
tempP_NonOrg <- data %>% filter(., class=="nonorganic") %>% select(., pX, pY)
colnames(tempP_NonOrg) <- c("p_X_nonorg", "p_Y_nonorg")
return(data.frame(tempQ, tempP_Org, tempP_NonOrg))
}

# Function that plots the loglog and actual curves
crossPEDLinearReg <- function(data, TYPES, log=TRUE) {
  Q <- data %>% select(oz) %>% {if (log) log(.) else (.)} %>% as.matrix()
  pXOrg <- data %>% select(p_X_org) %>% {if (log) log(.) else (.)} %>% {if ("xOrg" %in% TYPES) (.) else (.)*0} %>% as.matrix()
  pYOrg <- data %>% select(p_Y_org) %>% {if (log) log(.) else (.)} %>% {if ("yOrg" %in% TYPES) (.) else (.)*0}  %>% as.matrix()
  pXNonOrg <- data %>% select(p_X_nonorg) %>% {if (log) log(.) else (.)} %>% {if ("xNonOrg" %in% TYPES) (.) else (.)*0}  %>% as.matrix()
  pYNonOrg <- data %>% select(p_Y_nonorg) %>% {if (log) log(.) else (.)} %>% {if ("yNonOrg" %in% TYPES) (.) else (.)*0}  %>% as.matrix()
  return(lm(Q~pXOrg+pYOrg+pXNonOrg+pYNonOrg))
}


crossXOrg <- retrieveDataCPED(data, "organic", "X")
crossYOrg <- retrieveDataCPED(data, "organic", "Y")
crossXNonOrg <- retrieveDataCPED(data, "nonorganic", "X")
crossYNonOrg <- retrieveDataCPED(data, "nonorganic", "Y")

lmXOrg <- crossPEDLinearReg(crossXOrg, c("xOrg"))
summary(lmXOrg)

lmXOrg <- crossPEDLinearReg(crossXOrg, c("yOrg"))
summary(lmXOrg)

lmXOrg <- crossPEDLinearReg(crossXOrg, c("xNonOrg"))
summary(lmXOrg)

lmXOrg <- crossPEDLinearReg(crossXOrg, c("yNonOrg"))
summary(lmXOrg)
```

### Profit versus Price for the four products
```{r}
XOrg.Qcoef = c(-16.8432,-7.0398)
YOrg.Qcoef = c(-15.7803,-6.7308)
XNonOrg.Qcoef = c(-15.8704,-6.7511)
YNonOrg.Qcoef = c(-15.4133,-6.657)

XOrg.Ccoef = c(-0.0006,0.8491)
YOrg.Ccoef = c(0.0003,0.8042)
XNonOrg.Ccoef = c(-0.0004,0.8434)
YNonOrg.Ccoef = c(0.0003,0.804)

profit <- function(price, Qcoef, Ccoef) {
  quantity <- exp(Qcoef[1]) * price^Qcoef[2]
  cost <- Ccoef[1] + Ccoef[2]*price
  return(quantity*(price-cost))
}
Xorg.Profit.func <- function(price) {
  return(profit(price,XOrg.Qcoef,XOrg.Ccoef))
}
Yorg.Profit.func <- function(price) {
  return(profit(price,YOrg.Qcoef,YOrg.Ccoef))
}
Xnonorg.Profit.func <- function(price) {
  return(profit(price,XNonOrg.Qcoef,XNonOrg.Ccoef))
}
Ynonorg.Profit.func <- function(price) {
  return(profit(price,YNonOrg.Qcoef,YNonOrg.Ccoef))
}
ggplot(data.frame(price = c(0.018, 0.035)), aes(price)) + 
  stat_function(fun = Xorg.Profit.func, aes(colour = "organic X")) + 
  stat_function(fun = Yorg.Profit.func, aes(colour = "organic Y")) + 
  stat_function(fun = Xnonorg.Profit.func, aes(colour = "inorganic X")) + 
  stat_function(fun = Ynonorg.Profit.func, aes(colour = "inorganic Y")) +
  scale_colour_manual("Lgend title", values = c("red", "blue", "green", "orange")) +
  labs(x = "price/oz", y = "profit/wk", title = "Profit per week versus price for each product")
```



### Marginal Cost = Marginal Revenue
```{r}
# Linear Model for C(q)
costQuantityLM <- function(data, CLASS, BRAND) {
  cost <- data %>% filter(class==CLASS, brand==BRAND) %>% select(c) %>% log() %>% as.matrix()
  quantity <- data %>% filter(class==CLASS, brand==BRAND) %>% select(oz) %>% log() %>% as.matrix()
  return(lm(cost~quantity))
}

# Linear Model for R(q)
revenueQuantityLM <- function(data, CLASS, BRAND) {
  revenue <- data %>% filter(class==CLASS, brand==BRAND) %>% select(p) %>% log() %>% as.matrix()
  quantity <- data %>% filter(class==CLASS, brand==BRAND) %>% select(oz) %>% log() %>% as.matrix()
  return(lm(revenue~quantity))
}

marginalValue <- function(point, coef) {
  return(exp(coef[1])*point^coef[2] + coef[2]*exp(coef[1])*point^(coef[2]-1)*point)
}

cQ_X_org <- costQuantityLM(data.ref, "organic", "X")
cQ_X_org$coefficients[1] <- cQ_X_org$coefficients[1]
cQ_X_org$coefficients[2] <- cQ_X_org$coefficients[2]/1.15
cQ_Y_org <- costQuantityLM(data.ref, "organic", "Y")
cQ_X_nonorg <- costQuantityLM(data.ref, "nonorganic", "X")
cQ_Y_nonorg <- costQuantityLM(data.ref, "nonorganic", "Y")

rQ_X_org <- revenueQuantityLM(data.ref, "organic", "X")
rQ_Y_org <- revenueQuantityLM(data.ref, "organic", "Y")
rQ_X_nonorg <- revenueQuantityLM(data.ref, "nonorganic", "X")
rQ_Y_nonorg <- revenueQuantityLM(data.ref, "nonorganic", "Y")

cQ_XO_Curve <- function(quantity) return(marginalValue(quantity,cQ_X_org$coefficients))
rQ_XO_Curve <- function(quantity) return(marginalValue(quantity,rQ_X_org$coefficients))

cQ_YO_Curve <- function(quantity) return(marginalValue(quantity,cQ_Y_org$coefficients))
rQ_YO_Curve <- function(quantity) return(marginalValue(quantity,rQ_Y_org$coefficients))

cQ_XI_Curve <- function(quantity) return(marginalValue(quantity,cQ_X_nonorg$coefficients))
rQ_XI_Curve <- function(quantity) return(marginalValue(quantity,rQ_X_nonorg$coefficients))

cQ_YI_Curve <- function(quantity) return(marginalValue(quantity,cQ_Y_nonorg$coefficients))
rQ_YI_Curve <- function(quantity) return(marginalValue(quantity,rQ_Y_nonorg$coefficients))

quantity.range = c(10, 100000)
ggplot(data.frame(quantity = quantity.range ), aes(quantity)) + 
  stat_function(fun = cQ_XO_Curve, aes(colour = "MC XO")) + 
  stat_function(fun = rQ_XO_Curve, aes(colour = "MR XO")) + 
  labs(y = "price/cost (per oz)", x="Quantity", title = "MC and MR for Organic X")

ggplot(data.frame(quantity = quantity.range ), aes(quantity)) + 
  stat_function(fun = cQ_YO_Curve, aes(colour = "MC YO")) + 
  stat_function(fun = rQ_YO_Curve, aes(colour = "MR YO")) + 
  labs(y = "price/cost (per oz)", x="Quantity", title = "MC and MR for Organic Y")

ggplot(data.frame(quantity = quantity.range ), aes(quantity)) + 
  stat_function(fun = cQ_XI_Curve, aes(colour = "MC XI")) + 
  stat_function(fun = rQ_XI_Curve, aes(colour = "MR XI")) + 
  labs(y = "price/cost (per oz)", x="Quantity", title = "MC and MR for NonOrganic X")

ggplot(data.frame(quantity = quantity.range ), aes(quantity)) + 
  stat_function(fun = cQ_YI_Curve, aes(colour = "MC YI")) + 
  stat_function(fun = rQ_YI_Curve, aes(colour = "MR YI")) + 
  labs(y = "price/cost (per oz)", x="Quantity", title = "MC and MR for NonOrganic Y")
```

### MC = MR fake data
Reduced cost/oz response to an increase in quantity by 15% to reflect a greater fixed cost. 
```{r}
cQ_X_org <- costQuantityLM(data.ref, "organic", "X")
cQ_X_org$coefficients[1] <- cQ_X_org$coefficients[1]
cQ_X_org$coefficients[2] <- cQ_X_org$coefficients[2]/1.15
cQ_XO_Curve <- function(quantity) return(marginalValue(quantity,cQ_X_org$coefficients))
rQ_XO_Curve <- function(quantity) return(marginalValue(quantity,rQ_X_org$coefficients))
quantity.range = c(10, 100000)
ggplot(data.frame(quantity = quantity.range ), aes(quantity)) + 
  stat_function(fun = cQ_XO_Curve, aes(colour = "MC XO")) + 
  stat_function(fun = rQ_XO_Curve, aes(colour = "MR XO")) + 
  labs(y = "price/cost (per oz)", x="Quantity", title = "MC and MR for Organic X (with improved c curve)")

ggplot(data.frame(quantity = quantity.range ), aes(quantity)) + 
  stat_function(fun = cQ_XO_Curve, aes(colour = "MC XO")) + 
  stat_function(fun = rQ_XO_Curve, aes(colour = "MR XO")) + 
  labs(y = "log10 price/cost (per oz)", x="log 10 Quantity", title = "MC and MR for Organic X (with improved c curve)") +
  scale_x_log10()
```

### Multivariate cross-PED
```{r}
crossPEDLM <- function(data.ref, BRAND="X", CLASS="organic") {
  quantity <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(oz) %>% log() %>% as.matrix()
  hVal <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(Hval) %>% log() %>% as.matrix()
  XO_org_price <- data.ref %>% filter(brand=="X", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  YO_org_price <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  XI_org_price <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  YI_org_price <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  XO_org_deal <- data.ref %>% filter(brand=="X", class=="organic") %>% select(deal) %>% as.matrix()
  YO_org_deal <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(deal) %>% as.matrix()
  XI_org_deal <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(deal) %>% as.matrix()
  YI_org_deal <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(deal) %>% as.matrix()
  
  lm.crossPED <- lm(quantity~hVal + XO_org_price + YO_org_price + XI_org_price + YI_org_price + XO_org_deal + YO_org_deal + XI_org_deal + YI_org_deal)
}
```

### Multivariate cross-PED for XO
```{r}
crossPEDLMXO <- function(data.ref, BRAND="X", CLASS="organic") {
  quantity <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(oz) %>% log() %>% as.matrix()
  hVal <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(Hval) %>% log() %>% as.matrix()
  XO_org_price <- data.ref %>% filter(brand=="X", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  YO_org_price <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  XI_org_price <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  YI_org_price <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  XO_org_deal <- data.ref %>% filter(brand=="X", class=="organic") %>% select(deal) %>% as.matrix()
  YO_org_deal <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(deal) %>% as.matrix()
  XI_org_deal <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(deal) %>% as.matrix()
  YI_org_deal <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(deal) %>% as.matrix()
  
  lm.crossPED <- lm(quantity~XO_org_price + XO_org_deal + YO_org_deal)
}
XO_cross_PED <- crossPEDLM(data.ref, "X", "organic")
summary(XO_cross_PED)
XO_cross_PED <- crossPEDLMXO(data.ref, "X", "organic")
summary(XO_cross_PED)
```
### Multivariate cross-PED for YO
```{r}
crossPEDLMYO <- function(data.ref, BRAND="Y", CLASS="organic") {
  quantity <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(oz) %>% log() %>% as.matrix()
  hVal <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(Hval) %>% log() %>% as.matrix()
  XO_org_price <- data.ref %>% filter(brand=="X", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  YO_org_price <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  XI_org_price <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  YI_org_price <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  XO_org_deal <- data.ref %>% filter(brand=="X", class=="organic") %>% select(deal) %>% as.matrix()
  YO_org_deal <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(deal) %>% as.matrix()
  XI_org_deal <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(deal) %>% as.matrix()
  YI_org_deal <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(deal) %>% as.matrix()
  
  lm.crossPED <- lm(quantity~XO_org_price + YO_org_price + YO_org_deal)
}
YO_cross_PED <- crossPEDLM(data.ref, "Y", "organic")
summary(YO_cross_PED)
YO_cross_PED <- crossPEDLMYO(data.ref, "Y", "organic")
summary(YO_cross_PED)
```
### Multivariate cross-PED for XI
```{r}
crossPEDLMXI <- function(data.ref, BRAND="X", CLASS="nonorganic") {
  quantity <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(oz) %>% log() %>% as.matrix()
  hVal <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(Hval) %>% log() %>% as.matrix()
  XO_org_price <- data.ref %>% filter(brand=="X", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  YO_org_price <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  XI_org_price <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  YI_org_price <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  XO_org_deal <- data.ref %>% filter(brand=="X", class=="organic") %>% select(deal) %>% as.matrix()
  YO_org_deal <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(deal) %>% as.matrix()
  XI_org_deal <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(deal) %>% as.matrix()
  YI_org_deal <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(deal) %>% as.matrix()
  
  lm.crossPED <- lm(quantity~XI_org_price + YI_org_price + XI_org_deal)
}
XI_cross_PED <- crossPEDLM(data.ref, "X", "nonorganic")
summary(XI_cross_PED)
XI_cross_PED <- crossPEDLMXI(data.ref, "X", "nonorganic")
summary(XI_cross_PED)
```

### Multivariate cross-PED for YI
```{r}
crossPEDLMYI <- function(data.ref, BRAND="Y", CLASS="nonorganic") {
  quantity <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(oz) %>% log() %>% as.matrix()
  hVal <- data.ref %>% filter(brand==BRAND, class==CLASS) %>% select(Hval) %>% log() %>% as.matrix()
  XO_org_price <- data.ref %>% filter(brand=="X", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  YO_org_price <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(p) %>% log() %>% as.matrix()
  XI_org_price <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  YI_org_price <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(p) %>% log() %>% as.matrix()
  XO_org_deal <- data.ref %>% filter(brand=="X", class=="organic") %>% select(deal) %>% as.matrix()
  YO_org_deal <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(deal) %>% as.matrix()
  XI_org_deal <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(deal) %>% as.matrix()
  YI_org_deal <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(deal) %>% as.matrix()
  
  lm.crossPED <- lm(quantity~XI_org_price + YI_org_price + YI_org_deal)
}
YI_cross_PED <- crossPEDLM(data.ref, "Y", "nonorganic")
summary(YI_cross_PED)
YI_cross_PED <- crossPEDLMYI(data.ref, "Y", "nonorganic")
summary(YI_cross_PED)
```

# General Statistics
```{r}
data.ref <- data.ref %>% mutate(profit=oz*(p-c))
# organic X
XO_oz_total <- data.ref %>% filter(brand=="X", class=="organic") %>% select(oz) %>% sum() 
XO_profit_total <- data.ref %>% filter(brand=="X", class=="organic") %>% select(profit) %>% sum() 
XO_oz_mean <- XO_oz_total/(52*7)
XO_profit_mean <- XO_profit_total/(52*7) 

# organic Y
YO_oz_total <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(oz) %>% sum() 
YO_profit_total <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(profit) %>% sum() 
YO_oz_mean <- YO_oz_total/(52*7)
YO_profit_mean <- YO_profit_total/(52*7)

# nonorganic X
XI_oz_total <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(oz) %>% sum() 
XI_profit_total <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(profit) %>% sum() 
XI_oz_mean <- XI_oz_total/(52*7)
XI_profit_mean <- XI_profit_total/(52*7)  

# nonorganic Y
YI_oz_total <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(oz) %>% sum() 
YI_profit_total <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(profit) %>% sum() 
YI_oz_mean <- YI_oz_total/(52*7)
YI_profit_mean <- YI_profit_total/(52*7) 
```

value | organic X | organic Y | nonorganic X | nonorganic Y
------|-----------|-----------|--------------|-------------
Total oz | `r XO_oz_total` | `r YO_oz_total` | `r XI_oz_total` | `r YI_oz_total`
Total profit | `r XO_profit_total` | `r YO_profit_total` | `r XI_profit_total` | `r YI_profit_total`
Average oz | `r XO_oz_mean` | `r YO_oz_mean` | `r XI_oz_mean` | `r YI_oz_mean`
Average profit | `r XO_profit_mean` | `r YO_profit_mean` | `r XI_profit_mean` | `r YI_profit_mean``


## Boxplots of Product Price and Oz
```{r}
summary_XO <- data.ref %>% filter(brand=="X", class=="organic") %>% select(oz, p, c, deal, feat)
summary_XO <- mutate(summary_XO, profit=oz*(p-c))
summary_XO$deal[summary_XO$deal == 0] <- "Without"
summary_XO$deal[summary_XO$deal == 1] <- "With"
summary_XO$feat[summary_XO$feat == 0] <- "Without"
summary_XO$feat[summary_XO$feat == 1] <- "With"
ggplot(summary_XO, aes(x=deal, y=profit)) + geom_boxplot() + labs(title="XO profit with and without a deal", x="Deal", y = "Profit") 

ggplot(summary_XO, aes(x=deal, y=oz)) + geom_boxplot() + labs(title="XO oz sold with and without a deal", x="Deal", y = "Oz") 

ggplot(summary_XO, aes(x=feat, y=profit)) + geom_boxplot() + labs(title="XO profit with and without a feature", x="Feature", y = "Profit") 

ggplot(summary_XO, aes(x=feat, y=oz)) + geom_boxplot() + labs(title="XO oz sold with and without a feature", x="Feature", y = "Oz") 

summary_YO <- data.ref %>% filter(brand=="Y", class=="organic") %>% select(oz, p, c, deal, feat)
summary_YO <- mutate(summary_YO, profit=oz*(p-c))
summary_YO$deal[summary_YO$deal == 0] <- "Without"
summary_YO$deal[summary_YO$deal == 1] <- "With"
summary_YO$feat[summary_XO$feat == 0] <- "Without"
summary_YO$feat[summary_XO$feat == 1] <- "With"
ggplot(summary_YO, aes(x=deal, y=profit)) + geom_boxplot() + labs(title="YO profit with and without a deal", x="Deal", y = "Profit") 

ggplot(summary_YO, aes(x=deal, y=oz)) + geom_boxplot() + labs(title="YO oz sold with and without a deal", x="Deal", y = "Oz") 

ggplot(summary_YO, aes(x=feat, y=profit)) + geom_boxplot() + labs(title="YO profit with and without a feature", x="Feature", y = "Profit") 

ggplot(summary_YO, aes(x=feat, y=oz)) + geom_boxplot() + labs(title="YO oz sold with and without a feature", x="Feature", y = "Oz") 

summary_XI <- data.ref %>% filter(brand=="X", class=="nonorganic") %>% select(oz, p, c, deal, feat)
summary_XI <- mutate(summary_XI, profit=oz*(p-c))
summary_XI$deal[summary_XI$deal == 0] <- "Without"
summary_XI$deal[summary_XI$deal == 1] <- "With"
summary_XI$feat[summary_XI$feat == 0] <- "Without"
summary_XI$feat[summary_XI$feat == 1] <- "With"
ggplot(summary_XI, aes(x=deal, y=profit)) + geom_boxplot() + labs(title="XI profit with and without a deal", x="Deal", y = "Profit") 

ggplot(summary_XI, aes(x=deal, y=oz)) + geom_boxplot() + labs(title="XI oz sold with and without a deal", x="Deal", y = "Oz") 

ggplot(summary_XI, aes(x=feat, y=profit)) + geom_boxplot() + labs(title="XI profit with and without a feature", x="Feature", y = "Profit") 

ggplot(summary_XI, aes(x=feat, y=oz)) + geom_boxplot() + labs(title="XI oz sold with and without a feature", x="Feature", y = "Oz") 


summary_YI <- data.ref %>% filter(brand=="Y", class=="nonorganic") %>% select(oz, p, c, deal, feat)
summary_YI <- mutate(summary_YI, profit=oz*(p-c))
summary_YI$deal[summary_YI$deal == 0] <- "Without"
summary_YI$deal[summary_YI$deal == 1] <- "With"
summary_YI$feat[summary_YI$feat == 0] <- "Without"
summary_YI$feat[summary_YI$feat == 1] <- "With"
ggplot(summary_YI, aes(x=deal, y=profit)) + geom_boxplot() + labs(title="YI profit with and without a deal", x="Deal", y = "Profit") 

ggplot(summary_YI, aes(x=deal, y=oz)) + geom_boxplot() + labs(title="YI oz sold with and without a deal", x="Deal", y = "Oz") 


ggplot(summary_YI, aes(x=feat, y=profit)) + geom_boxplot() + labs(title="YI profit with and without a deal", x="Feature", y = "Profit") 

ggplot(summary_YI, aes(x=feat, y=oz)) + geom_boxplot() + labs(title="YI oz sold with and without a feature", x="Feature", y = "Oz") 
```




